On the use of relative brain size

### 2022-04-08 manuscript.Rmd
Starting to revise main text.

---
title: "On the use of relative brain size"
author: "Simeon Q. Smeele $^{1,2,3}$"
date: "March 2022"
output:
  word_document: default
  pdf_document: default
header-includes:
- \usepackage{lineno}
- \linenumbers
editor_options:
  chunk_output_type: console
bibliography: bibliography.bib
---

```{r include=FALSE}
# Libraries
## for installation instructions see the README
library(cmdstanr)
library(scales)

# Paths
path_response_stan = 'response.stan' # models
path_predictor_stan = 'predictor.stan'
path_sem_stan = 'sem.stan'
path_pdf_response = 'response.pdf' # pdfs
path_pdf_predictor = 'predictor.pdf'
```

@@

@@

I simulated 20 datasets per case and present parameter estimates for all datasets. Frequentist linear models were fitted with the *lm* function from base R [@R]. Bayesian models were fitted using the *cmstanr* package [@cmdstanr], which runs the No U-turn Sampler in Stan [@gelman2015stan] with four chains and default sampler settings.

@@

>>>>

---
title: "On the use of relative brain size"
author: "Simeon Q. Smeele $^{1,2,3}$"
date: "April 2022"
output:
  pdf_document: default
  word_document: default
header-includes:
- \usepackage{lineno}
- \linenumbers
editor_options:
  chunk_output_type: console
bibliography: bibliography.bib
---

```{r include=FALSE}
# Libraries
## for installation instructions see the README
library(cmdstanr)
library(scales)
library(daggity)

# Paths
path_response_stan = 'response.stan' # models
path_predictor_stan = 'predictor.stan'
path_sem_stan = 'sem.stan'
path_pdf_response = 'figures/response.pdf' # pdfs
path_pdf_predictor = 'figures/predictor.pdf'
```

@@

```{r echo=FALSE}
# Make DAG
dag <- dagitty("dag {body_size -> relative_brain_size <- z}")
plot( graphLayout( dag ) )
```

@@

I simulated 20 datasets per case and present parameter estimates for all datasets. Frequentist linear models were fitted with the *lm* function from base R [@R]. Bayesian models were fitted using the *cmstanr* package [@cmdstanr], which runs the No U-turn Sampler in Stan [@gelman2015stan] with four chains and default sampler settings (1000 warmup and 1000 sampling iterations). Rhat, divergent transitions and effective sample size were monitored by the package and any issues were reported.

To test if sample size had an effect on which model performed best, additional simulations were run and analysed for 20 and 1000 species (see supplemental results). To test if better or worse priors had an affect on which model performed best, and the performance of the best model, additional simulations were run with informative and vague priors (see supplemental materials).

@@

Results were similar for simulations with smaller and larger sample sizes (see supplemental materials. Results were also similar for models with vague and informative prior (see supplemental materials). The informative priors constrained the Bayesian linear models estimate of the body size effect to positive values, but none of the posterior distributions included the true value of the body size effect. In other words, even if the model is run with the correct value as prior, it estimates the effect to be absent.
